Automatic detection of bad habits of programming in Scratch

### 2014-04-17 paperFIE_en.tex
Fix errata

\paragraph{}In our work as teachers with high school students, we found that, despite our constant insistence and warnings to try to avoid them, many students show two bad habits in a regular basis that have to do with named object and code repetition.

@@

\paragraph{}Regarding the named object it is curious that Scratch users name correctly, ie significantly, the variables used in their projects. In our opinion the reason to explain this paradox is because it is mandatory to assign a name to a variable the moment it is created, as the environment does not name it by default. However, when creating a new character a  \textit{SpriteX} name is assigned automatically. A change on this feature of the environment, obliguing users to name new objects, would eliminate this malpractice.
\paragraph{}Regarding the code repetition and low usage Scratch users make of creating their own blocks (the equivalent of defining methods or procedures in other languages), works as the one performed by Seiter and Foreman \cite {seiter2013modeling}, in which they show that abstraction and modularization capacities are concepts that seem to be developed from a certain age, may explain the low rates of use of this functionality, since a significant part of the Scratch community consists of children under 10 years old \footnote{http://scratch.mit.edu/statistics/\#age}. Future studies should further investigate this line to continue advancing in the definition of an appropriate framework for different ages and to check whether users learning online and those who do it in a regulated environment show different use rates of this functionality .

>>>>

\paragraph{}In our work as teachers with high school students, we found that, despite our constant insistence and warnings to try to avoid them, many students show two bad habits in a regular basis that have to do with object namig and code repetition.

@@

\paragraph{}Regarding the object namig it is curious that Scratch users name correctly, ie significantly, the variables used in their projects. In our opinion the reason to explain this paradox is because it is mandatory to assign a name to a variable the moment it is created, as the environment does not name it by default. However, when creating a new character a  \textit{SpriteX} name is assigned automatically. A change on this feature of the environment, obliguing users to name new objects, would eliminate this malpractice.
\paragraph{}Regarding the code repetition and low usage Scratch users make of creating their own blocks (the equivalent of defining methods or procedures in other languages), works as the one performed by Seiter and Foreman \cite {seiter2013modeling}, in which they show that abstraction and modularization capacities are concepts that seem to be developed from a certain age, may explain the low rates of use of this functionality, since a significant part of the Scratch community consists of children under 10 years old \footnote{http://scratch.mit.edu/statistics/\#age}. Future studies should further investigate this line to continue advancing in the definition of an appropriate framework for different ages and to check whether users learning online and those who do it in a regulated environment show different use rates of this functionality.
